---
title: "Uisng Ratio to Camparing US to EU Countries"
author: "David J Jackson"
date: "6/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(RSQLite)
library(tidyverse)
```

### Countries in The EU

* Austria, Belgium, Bulgaria, Croatia, 
* Republic of Cyprus, Czech Republic, Denmark, 
* Estonia, Finland, France, Germany, 
* Greece, Hungary, Ireland, Italy, 
* Latvia, Lithuania, Luxembourg, Malta, 
* Netherlands, Poland, Portugal, Romania, 
* Slovakia, Slovenia, Spain and Sweden.

## Using Ratios to compare US COVID-19 stats to Another Country

```{r, echo=FALSE}
rm(list=ls())
db <- dbConnect(SQLite(), dbname="../COVIDDB/CORVID.sqlite3")
ECDC <- dbGetQuery(db, "SELECT Countries,Population FROM ECDC")
ECDC <- ECDC %>% select(Countries,Population)  %>% group_by(Countries,Population) %>% summarise(Count =n())

EU <- data.table::fread("../db/EU_countries.csv")
```

```{r}
JHU <- dbGetQuery(db, "SELECT country,confirmed,deaths FROM JHUDATA WHERE date ='2020-06-29'")
dbDisconnect(db)
```

### Combine EU Counties with ECDC and JHU 

```{r,echo=FALSE}
DATA <- left_join(EU,ECDC,by="Countries")
colnames(DATA) <- c("country","Population","Count")
ATAD <- left_join(DATA,JHU,by="country")
```

### Reported Cases(Using Ratio)
* A = US Population
* B = US Cases/Deaths
* C = Target Country Population
* X = Predicted Cases/Deaths

```{r, echo=FALSE}
A = 331000000 # US Population
B = 126000    # US cases
C = 66647112   # Great Britan
#   # -----------------
# A:B = C:X
X =(B*C)/A
X

```

### Reported Deaths (Using Ratio)

```{r, echo=FALSE}
A = 331000000 # US Population
B = 126140    # US Deaths
C = 66647112   # Great Britain
#   # -----------------
# A:B = C:X
X =(B*C)/A
X
```

## New with Population Ratio
```{r}
X = (A/C) * B
X
```